cardinalR: Generating interesting high-dimensional data structures

### 2025-07-06 paper-cardinalR.Rmd
Added some multicluster examples

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau"), 
                        exp = c("",
                                ""))
```

@@

The package includes various supplementary tools in addition to the shape-generating functions mentioned earlier. These tools allow users to generate noise dimensions with a normal distribution and various wavy patterns, create background noise, randomize the rows of the data, reposition clusters, generate a vector whose product and sum are approximately equal to a target value, rotate structures, and normalize the data. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:add-tb-html)', '\\@ref(tab:add-tb-pdf)'))` details these functions.

>>>>

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau",
                                "make_curvygau",
                                "make_multigrid",
                                "make_threeclust01",
                                "make_fourclust01",
                                "make_fiveclust01"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                "",
                                "",
                                ""))
```

@@

The package includes various supplementary tools in addition to the shape generating functions mentioned earlier. These tools allow users to generate noise dimensions with a normal distribution and various wavy patterns, create background noise, randomize the rows of the data, reposition clusters, generate a vector whose product and sum are approximately equal to a target value, rotate structures, and normalize the data. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:add-tb-html)', '\\@ref(tab:add-tb-pdf)'))` details these functions.

### 2025-07-06 paper-cardinalR.tex
Added some multicluster examples

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
make\_mobiusgau & \\
make\_multigau & \\
\bottomrule
\end{tabular}
\end{table}

@@

The package includes various supplementary tools in addition to the shape-generating functions mentioned earlier. These tools allow users to generate noise dimensions with a normal distribution and various wavy patterns, create background noise, randomize the rows of the data, reposition clusters, generate a vector whose product and sum are approximately equal to a target value, rotate structures, and normalize the data. Table \ref{tab:add-tb-pdf} details these functions.

>>>>

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
make\_mobiusgau & \\
make\_multigau & \\
make\_curvygau & \\
make\_threeclust01 & \\
make\_fourclust01 & \\
\addlinespace
make\_fiveclust01 & \\
\bottomrule
\end{tabular}
\end{table}

@@

The package includes various supplementary tools in addition to the shape generating functions mentioned earlier. These tools allow users to generate noise dimensions with a normal distribution and various wavy patterns, create background noise, randomize the rows of the data, reposition clusters, generate a vector whose product and sum are approximately equal to a target value, rotate structures, and normalize the data. Table \ref{tab:add-tb-pdf} details these functions.
